Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-03-31 paper/src/paper.tex
u

Parallel job scheduling is a old studied theoretical
problem~\cite{Frachtenberg:2009:JSS:1692356} \textcolor{orange}{(cite
feitelson-rudolph-swiegelshon)} whose practical ramifications, varying
hypotheses, and inherent uncertainty of the problem applied on the HPC field
have driven practitioners to use simple heuristics (and researchers to
study their behavior). The two most popular heuristics for HPC platforms are
EASY~\cite{easy} and Conservative~\cite{Mu'alem:2001:UPW:380314.380315}
backfillings.

@@

\subsection{Notes}
This artefact description was prepared according to the guidelines located at \url{http://ctuning.org/ae/submission.html}
\end{document}

>>>>

Parallel job scheduling is a old studied theoretical
problem~\cite{Frachtenberg:2009:JSS:1692356,Feitelson:2004:PJS:2128864.2128865}
whose practical ramifications, varying hypotheses, and inherent uncertainty of
the problem applied on the HPC field have driven practitioners to use simple
heuristics (and researchers to study their behavior). The two most popular
heuristics for HPC platforms are EASY~\cite{easy} and
Conservative~\cite{Mu'alem:2001:UPW:380314.380315} backfillings.

@@

\subsection{Notes}

This artefact description was prepared according to the guidelines located at
\url{http://ctuning.org/ae/submission.html}

\end{document}
